Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-01-31 TACAS2018/paper.tex
cite package
wording intro

\usepackage{microtype}
\usepackage{graphicx}
\usepackage{color}
\usepackage{amssymb}
\usepackage{amsmath}
%\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{framed}
\usepackage{listings}
\usepackage{algorithm,algpseudocode}
\usepackage{epstopdf}
\usepackage{pifont}
\usepackage{todonotes}
\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
\usetikzlibrary{patterns}
\usepackage{url}
\usepackage{mathtools}

@@

Modern implementations of embedded control systems have proliferated with
the availability of low-cost devices that can perform highly non-trivial
control tasks, with significant impact in numerous application areas such as
life sciences, environmental control and robotics~\cite{astrom1997computer,
Franklin15}.  Correct synthesis is non-trivial, even in cases with
restricted dynamics.  We examine the case of Linear Time Invariant (LTI)
models, for which the synthesis of controllers is well understood.  However,
the use of digital control architectures adds new challenges caused by
artifacts specific to digital control, such as the effects of
finite-precision arithmetic (referred to here as Finite Word Length or FWL
effects), time discretization and quantization errors introduced by A/D and
D/A conversion.

While research on digital control is well
developed~\cite{astrom1997computer}, automated and sound control synthesis
is challenging, particularly when the synthesis objective goes beyond
classical stability.  Recent work~\cite{abate2017automated} described a
method for synthesizing safe digital stabilizing controllers for fully
observable LTI plants.  This work differs from the vast majority of existing
approaches in that it explores the continuous space of the system to
synthesize correct by construction minimal digital controllers.  Contrary to
LTL models that require thousands of states and elaborate algorithms to
implement \cite{reissig2017feedback}, these PID-like controllers are
represented by a few parameters and only require a few lines of code, thus
reducing the implementation cost and execution time while remaining
resilient to the effects of digitalization. 
However,~\cite{abate2017automated}~is restricted to fully observed systems
(i.e., where all the states are known) modeled in discrete time, and
furthermore explores only a limited set of properties that engineers are
interested in.  Conversely, in most real implementations, the internal state
of a plant cannot be directly measured but rather inferred from its effect
on the output.  A plant model that minimizes the difference between its
output and the real plant output is called an observer and it is a well
known paradigm in the control literature~\cite{astrom1997computer}.

In this paper we build on the ideas presented in~\cite{abate2017automated}
and develop a new technique that addresses most of these limitations. 
By~combining state-of-the-art synthesis and verification engines we
automatically generate digital observer controllers for a given continuous
plant model that are correct by construction.  %% This approach delivers a high
%% degree of automation, promises to reduce the cost and time of development of
%% digital control dramatically, and requires considerably less expertise than
%% a-posteriori verification.
%
Specifically, we synthesize stable, software-implemented embedded
controllers along with a model of a physical plant (observer).  Due to the
complexity of such closed-loop systems, we focus on linear models with known
configurations, and perform parametric synthesis of controllers meeting a
number of properties that define their desired behavior.

>>>>

\usepackage{microtype}
\usepackage{graphicx}
\usepackage{color}
\usepackage{amssymb}
\usepackage{amsmath}
%\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{framed}
\usepackage{listings}
\usepackage{algorithm,algpseudocode}
\usepackage{epstopdf}
\usepackage{pifont}
\usepackage{todonotes}
\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
\usetikzlibrary{patterns}
\usepackage{url}
\usepackage{mathtools}
\usepackage{cite}

@@

Modern implementations of embedded control systems have proliferated with
the availability of low-cost devices that can perform highly non-trivial
control tasks, with significant impact in numerous application areas such as
life sciences, environmental control and robotics~\cite{astrom1997computer,
Franklin15}.  Correct synthesis of control software for such platforms is
non-trivial, even in cases with restricted dynamics.  We consider the case
of Linear Time Invariant (LTI) models, for which the synthesis of
controllers is well understood.  However, the use of digital control
architectures adds new challenges caused by artifacts specific to digital
control, such as the effects of finite-precision arithmetic (referred to
here as Finite Word Length or FWL effects), time discretization and
quantization errors introduced by A/D and D/A conversion.

While research on digital control is well
developed~\cite{astrom1997computer}, automated and sound control synthesis
is challenging, particularly when the synthesis objective goes beyond
classical stability.  Recent work~\cite{abate2017automated} described a
method for synthesizing safe digital stabilizing controllers for fully
observable LTI plants.  This work differs from the vast majority of existing
approaches in that it explores the continuous space of the system to
synthesize correct-by-construction minimal digital controllers.  In contrast
to LTL models, which require thousands of states and elaborate algorithms to
implement~\cite{reissig2017feedback}, these PID-like controllers are
represented by a few parameters and only require few lines of code, thus
reducing the implementation cost and execution time while remaining
resilient to the effects of digitalization. 
However,~\cite{abate2017automated}~is restricted to fully observed systems
(i.e., where all the states are known) modeled in discrete time, and
furthermore explores only a subset of the properties that engineers are
interested in.  By contrast, in most real implementations, the internal
state of a plant cannot be directly measured but has to be inferred from its
effect on the output.  A plant model that minimizes the difference between
its output and the real output of the plant is called an \emph{observer} and
it is a well known paradigm in the control
literature~\cite{astrom1997computer}.

In this paper we build on the ideas presented in~\cite{abate2017automated}
and develop a new technique that addresses most of these limitations. 
By~combining state-of-the-art synthesis and verification engines we
automatically generate digital \emph{observer controllers} for a given
continuous plant model that are correct by construction.
%
%% This approach delivers a high
%% degree of automation, promises to reduce the cost and time of development of
%% digital control dramatically, and requires considerably less expertise than
%% a-posteriori verification.
%
Specifically, we synthesize stable, software-implemented embedded
controllers along with a model of a physical plant (observer).  Due to the
complexity of such closed-loop systems, we focus on linear models with known
configurations, and perform parametric synthesis of controllers meeting a
number of properties that define their desired behavior.
